---
title: "Data Wrangling"
author: "Yifan Shi"
date: "2024-09-17"
output: github_document
---

```{r setup, echo = FALSE, message = FALSE}
library(tidyverse)

```


This document will show how to import data

## Import the FAS Litters CSV

```{r}
litters_df = read_csv("data_import_examples/FAS_litters.csv")

litters_df = janitor::clean_names(litters_df)
```
not attaching the whole janitor package at the beginning because we are only using the clean_names function here 
clean_name fucntion convert everything to lower case, separated by _ 

## Look at the dataset
```{r}
litters_df

head(litters_df)
tail(litters_df, 10)
```

```{r eval = FALSE}
view(litters_df)
```

## Import the FAS pups CSV

Use reletive path
```{r}
pups_df = read_csv("data_import_examples/FAS_pups.csv")

pups_df = janitor::clean_names(pups_df)
```

Use absolute path

coln names and skipping 
```{r}
litters_df=
  read_csv(
    file="data_import_examples/FAS_litters.csv",
    skip=2
  )
```

## Look at the dataset
```{r}
pups_df

head(pups_df)
tail(pups_df, 10)
```

```{r eval = FALSE}
view(pups_df)
```



What about missing data

```{r}
litters_df=
  read_csv(
    file="data_import_examples/FAS_litters.csv",
    na = c("NA", " ", ".")
  )

litters_df = janitor::clean_names(litters_df)
pull(litters_df, gd0_weight)
```


